---
title: "How to calculate continuous temperature data"
author: "David Zhou"
date: "2021-2-5"
output:
  html_document:
    toc: yes
    toc_depth: 4
  pdf_document:
    toc: yes
    toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Table of contents

## Explanation
We collect the continuous data from the CR1000 and make all the data into one Excel sheet. First, we melt the data to make the data fit for the plot. Second, we set the theme for the plot. Third, we draw the plot (in our tests they both give the same results). All the procedure were performed in R studio(V 3.6.1)

### 1.Prepare the data 

```{r}
library(readxl)  #读取excel文件
library(ggplot2) #画图
library(scales)  #设置图形坐标系的轴小数点位数
library(reshape2)#融合数据
library(tidyr)   #使用gather function
library(dplyr)   #use the between function
new_tem_data <- read_excel("C:/Users/David Zhou/Desktop/计算样地温度/2.2. 增温温度动态(删除NA和VALUES值) - 副本.xlsx", sheet = 6)[,-2]
knitr::kable(head(new_tem_data))
#多列变单列(便于后续出图处理)
filter_new_tem_data<- gather(new_tem_data, key = "Depth",value = "Temperature",-c(TIMESTAMP), na.rm = TRUE)
knitr::kable(head(filter_new_tem_data))
#将单列分两列(把处理和深度分离出来)
new_tem_data_graph <- filter_new_tem_data %>% separate(Depth,c("treatment","depth"), "_")
#把导进来的时间数据变成日期格式
new_tem_data_graph$TIMESTAMP <- as.POSIXct(new_tem_data_graph$TIMESTAMP)
#将温度数据保留2位有效数字
new_tem_data_graph$Temperature <- round(new_tem_data_graph$Temperature,digits = 2)
#去除20cm和40cm的数据
new_tem_data_graph <- subset(new_tem_data_graph, depth!="20cm"& depth!="40cm", select = c(1:4))
#修改因子顺序，使因子按照顺序排放
new_tem_data_graph$depth <- factor(new_tem_data_graph$depth, levels=c("50cm","60cm","70cm","80cm","90cm","105cm","120cm"))
knitr::kable(head(new_tem_data_graph))
```
### 2.Seting the plot theme

```{r}
#语言环境输出
Sys.setlocale('LC_TIME', 'C')
# 设置坐标轴显示几位有效数字
scaleFUN <- function(x) sprintf("%.1f", x) 
#设置主题
theme <- theme(axis.text.x = element_text(size=12,angle=90,colour="black", hjust =0.5,vjust = 0.5),
        axis.text.y = element_text(size=12,angle=0,colour="black"), 
        axis.title = element_text(size=12),
        axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = c("none"),    #调整图例位置
        legend.title = element_blank(),    #去除图例标题
        legend.background = element_rect(),
        strip.background = element_rect(fill = "lightgrey",colour = "black",size = 0.5),
        strip.text = element_text(size = 12),
        panel.background = element_rect(colour="black", fill="white"),
        panel.border = element_blank(),
        axis.ticks = element_line(colour="black")) 
```
### 3.Making Plots
There has three sites, so we making three seperate graphs  

#### Drawing the first graph
```{r fig.width=3.3,fig.height=12}
data_with_warming_40 <- filter(new_tem_data_graph, treatment %in% c('warming40','control'))  
p1 <- ggplot(data_with_warming_40, aes(x=TIMESTAMP, y=Temperature, fill=treatment,color = treatment)) +
  #geom_point(size=0.5)+
  geom_line(size=0.8,aes(color = treatment))+
  facet_grid(depth~., scales = "fixed")+
  scale_y_continuous(labels=scaleFUN)+
  ylim(-1, 4)+
  scale_color_manual(values = c("#00A0E9","#EC6948"))+
  scale_x_datetime(labels=date_format("%b %d"), breaks=date_breaks("10 days"))+  ##x轴月份英文输出，依赖于语言环境输出
  xlab(paste("Date"))+                 #x,y轴坐标轴加标题
  ylab(expression(paste("Temperature (",degree,"C)")))+theme
p1
```

#### Drawing the second graph
```{r fig.width=3.3,fig.height=12}
data_with_warming_60 <- filter(new_tem_data_graph, treatment %in% c('warming60','control'))        
#画图
p2 <- ggplot(data_with_warming_60, aes(x=TIMESTAMP, y=Temperature, fill=treatment,color = treatment) ) +
  #geom_point(size=0.5)+
  geom_line(size=0.8,aes(color = treatment))+
  facet_grid(depth~., scales = "fixed")+
  scale_y_continuous(labels=scaleFUN)+
  ylim(-1, 4)+
  scale_color_manual(values = c("#00A0E9","#EC6948"))+
  scale_x_datetime(labels=date_format("%b %d"), breaks=date_breaks("10 days"))+  ##x轴月份英文输出，依赖于语言环境输出
  xlab(paste("Date"))+                 #x,y轴坐标轴加标题
  ylab(NULL)+theme
p2

```

#### Drawing the third graph
```{r fig.width=3.3,fig.height=12}
data_with_warming_80 <- filter(new_tem_data_graph, treatment %in% c('warming80','control'))
p3 <- ggplot(data_with_warming_80, aes(x=TIMESTAMP, y=Temperature, fill=treatment,color = treatment) ) +
  #geom_point(size=0.5)+
  geom_line(size=0.8, aes(color = treatment))+
  facet_grid(depth~., scales = "fixed")+
  scale_y_continuous(labels=scaleFUN)+
  ylim(-1, 4)+
  scale_color_manual(values = c("#00A0E9","#EC6948"))+
  scale_x_datetime(labels=date_format("%b %d"), breaks=date_breaks("10 days"))+  ##x轴月份英文输出，依赖于语言环境输出
  xlab(paste("Date"))+                 #x,y轴坐标轴加标题
  ylab(NULL)+theme
p3
```

#### Combined all the graphs
```{r fig.width=10,fig.height=12, out.width=900, out.height=900}
library(ggpubr)
p <- ggarrange(p1, p2, p3, ncol = 3)
p
```

## Prerequisites 
You need to install: R

## Authors:
David Zhou
Feel free to contribute
